SVG: The Paper

### 2022-07-19 Analysis/index.Rmd
plot edits
saving path length figure

plt1 + plt2 + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom', legend.title = element_blank())
```

@@

ggplot(path_lengths, aes(accuracy, prop_shorter, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(path_lengths, is_outlier == 0), 
              method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  scale_y_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) +
  coord_cartesian(ylim = c(0, 1)) -> plt2

plt1 + plt2 + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom')
```

>>>>

plt1 + plt2 + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom', legend.title = element_blank())

# regen with legend in a different position for saving to pdf (see below)
path_lengths %>% group_by(observer, type) %>%
  summarise(path_length = median(path_length), .groups = "drop") %>%
  ggplot(aes(path_length, fill = type)) + 
  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
  geom_vline(xintercept = 0, linetype = 2) + 
  theme(legend.position = "right") +
  scale_x_continuous("median path length") +
  scale_fill_manual(values = col3) -> plt2
```

@@

ggplot(path_lengths, aes(accuracy, prop_shorter, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(path_lengths, is_outlier == 0), 
              method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  scale_y_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) +
  coord_cartesian(ylim = c(0, 1)) -> plt2b

plt1 + plt2b + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom')
```

```{r}
ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 4)
```
